\documentclass[11pt,]{article}
\usepackage[sc, osf]{mathpazo}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}




\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% Now begins the stuff that I added.
% ----------------------------------

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\large\bf}
\subsectionfont{\rmfamily\mdseries\normalsize\itshape}


% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}


% Make parskips rather than indent with lists.
\usepackage{parskip}
\usepackage{titlesec}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}

% Use fontawesome. Note: you'll need TeXLive 2015. Update.
\usepackage{fontawesome}

% Fancyhdr, as I tend to do with these personal documents.
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0.0pt}
\renewcommand{\footrulewidth}{0.0pt}
\lhead{}
\chead{}
\rhead{}
\lfoot{
\cfoot{\scriptsize  Timothy A. Model - Curriculum Vitae }}
\rfoot{\scriptsize \thepage/{\hypersetup{linkcolor=black}\pageref{LastPage}}}

% Always load hyperref last.
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref

\hypersetup{unicode=true,
            pdftitle={Timothy A. Model:  Curriculum Vitae (Curriculum Vitae)},
            pdfauthor={Timothy A. Model},
            pdfkeywords={R Markdown, academic CV, template},
            colorlinks=true,
            linkcolor=Maroon,
            citecolor=Blue,
            urlcolor=Maroon,
            breaklinks=true, bookmarks=true}
\urlstyle{same}  % don't use monospace font for urls

\begin{document}


\centerline{\huge \bf Timothy A. Model}

\vspace{2 mm}

\hrule

\vspace{2 mm}

\moveleft.5\hoffset\centerline{Havighurst Fellow}
\moveleft.5\hoffset\centerline{Miami University, Oxford, OH}
\moveleft.5\hoffset\centerline{ \faEnvelopeO \hspace{1 mm} \href{mailto:}{\tt \href{mailto:tmodel@indiana.edu}{\nolinkurl{tmodel@indiana.edu}}} \hspace{1 mm}  \faGithub \hspace{1 mm} \href{http://github.com/timothymodel}{\tt timothymodel} \hspace{1 mm}    \faGlobe \hspace{1 mm} \href{http://timothymodel.com}{\tt timothymodel.com}   }

\vspace{2 mm}

\hrule


\hypertarget{employment}{%
\section{Employment}\label{employment}}

\emph{Havighurst Fellow} \hfill August 2019--Present \newline Havighurst
Center for Russian and Post-Soviet Studies \hfill \newline Department of
Global and Intercultural Studies \hfill \newline Miami University,
Oxford, OH

\hypertarget{education}{%
\section{Education}\label{education}}

\emph{Ph.D.~in Political Science} \hfill July 2019 \newline Indiana
University, Bloomington, IN \hfill \newline Fields: Comparative Politics
\& Quantitative Methods

\emph{B.A. in Diplomacy/Global Politics \& Russian, East European, and
Eurasian Studies} \hfill 2012 \newline Miami University, Oxford, OH

\hypertarget{research}{%
\section{Research}\label{research}}

\hypertarget{book-project}{%
\subsection{Book Project}\label{book-project}}

The Logic of Anti-Corruption Campaigns

\hypertarget{working-papers}{%
\subsection{Working Papers}\label{working-papers}}

Corruption Intolerance and Protest Mobilization (\emph{under review})
\hfill \newline Unpacking Anti-Corruption Purges \hfill \newline The
Short and Long-Term Effects of Anti-Corruption Activity on FDI
\hfill \newline The Differential Effects of Anti-Corruption Strategies

\hypertarget{presentations}{%
\subsection{Presentations}\label{presentations}}

American Political Science Association Annual Meeting \hfill 2019, 2018,
2017 \newline Association for Slavic, East European, \& Eurasian Studies
Convention \hfill 2019, 2018 \newline Moscow HSE-EACES Political Economy
Workshop \hfill 2019, 2017 \newline Midwest Political Science
Association Conference \hfill 2018 \newline Workshop on Urban Activism
\& the Development of Civil Society in Russia \hfill 2018 \newline
University of Wisconsin Russia Project Scholar's Workshop \hfill 2018
\newline Ostrom Workshop Colloquium \hfill 2016 \newline PSGSA Graduate
Student Conference \hfill 2015 \newline Havighurst Symposium on Putin's
Russia \hfill 2011

\hypertarget{other-publications}{%
\subsection{Other Publications}\label{other-publications}}

Calibration and characterization of intracellular Asante Potassium Green
probes, APG-2 and APG-4 (with Priyanka S. Rana, Brandon A. Gibbons,
Alexey A. Vereninov, Valentina E. Yurinskaya, Robert J. Clements, and
Michael A. Model). \emph{Analytical Biochemistry}. 2018.

\hypertarget{data-collection}{%
\subsection{Data Collection}\label{data-collection}}

Anti-Corruption Campaign Event Dataset \newline Moscow Housing
Development Survey \& Focus Group Study \newline Orange Revolution
Legacies Survey \newline Executive Approval Project

\hypertarget{fellowships-grants-awards}{%
\section{Fellowships, Grants, \&
Awards}\label{fellowships-grants-awards}}

\hypertarget{research-and-training}{%
\subsection{Research and Training}\label{research-and-training}}

Kennan Institute Title VIII Scholarship \hfill 2018 \newline Russian
Studies Workshop Collaborative Research Fellowship \hfill 2018 \newline
John V. Gillespie Memorial Scholarship \hfill 2018 \newline Russian
Studies Workshop Graduate Research Fellowship \hfill 2018 \newline
Russian Studies Workshop Predissertation Networking Fellowship
\hfill 2017 \newline Ostrom Workshop Graduate Student Research Award
\hfill 2016 \newline Katherine Greenough Fellowship for Best Graduate
Student Research Paper \hfill 2016 \newline Foreign Language and Area
Studies Fellowship \hfill 2014 \newline Department of Political Science
Fellowship \hfill 2014 \newline Mabel LaDuke Lauder Fellowship
\hfill 2013 \newline Havighurst Travel Grant \hfill 2011

\hypertarget{teaching}{%
\subsection{Teaching}\label{teaching}}

Department of Political Science Selection for Lieber Memorial Teaching
Award \hfill 2018 \newline Outstanding Associate Instructor Award
\hfill 2017

\hypertarget{service}{%
\subsection{Service}\label{service}}

Department of Political Science Graduate Leadership Award \hfill 2017

\hypertarget{conference-travel}{%
\subsection{Conference Travel}\label{conference-travel}}

HSE-EACES Summer Workshop Travel Grant \hfill 2019 \newline Graduate and
Professional Student Government Travel Award \hfill 2018 \newline
American Political Science Association Meeting Travel Grant \hfill 2018,
2017 \newline Russian Studies Workshop ASEEES Travel Grant \hfill 2017,
2016 \newline College of Arts and Sciences Conference Travel Award
\hfill 2017 \newline Department of Poltiical Science Conference Travel
Award \hfill 2017 \newline Center on American Politics Conference Travel
Grant \hfill 2017

\hypertarget{teaching-experience}{%
\section{Teaching Experience}\label{teaching-experience}}

\hypertarget{instructor-of-record}{%
\subsection{Instructor of Record}\label{instructor-of-record}}

ITS 201 Introduction to International Studies. Miami University.
\hfill Fall 2019 \newline POLS-Y 200 Politics of Corruption. Indiana
University. \hfill Spring 2017 \newline POLS-Y 205 Analyzing Politics
(Research Methods). Indiana University. \hfill Fall 2016

\hypertarget{teaching-assistant}{%
\subsection{Teaching Assistant}\label{teaching-assistant}}

POLS-Y 205 Analyzing Politics. Indiana University. \hfill Fall 2017,
Fall \& Spring 2015, Fall 2014 \newline POLS-Y 332 Russian Politics.
Indiana University. \hfill Spring 2016 \newline POLS-Y 105 Introduction
to Political Theory. Indiana University. \hfill Spring 2016 \newline
POLS-Y 100 American Political Controversies. Indiana University.
\hfill Fall 2013

\hypertarget{teaching-training-certifications}{%
\subsection{Teaching Training \&
Certifications}\label{teaching-training-certifications}}

Pedagogy Training II. Indiana University. \hfill Fall 2016 \newline
Pedagogy Training I. Indiana University. \hfill Fall 2013--Spring 2014

\hypertarget{skills-qualifications}{%
\section{Skills \& Qualifications}\label{skills-qualifications}}

Programming: \textsf{R}, Python, Stata, JAGS \hfill \newline Languages:
English (native), Russian (professional), Spanish (elementary)

\end{document}